---
title: "Ryne Swift Stat 3904 Project"
output: html_document
---



Bivariate Normal Map of Winnipeg
```{r}
#install.packages("mvtnorm")
library(mvtnorm)


set.seed(3006)                  
#Setting this seed as it yields a map that resembles Winnipeg.


#Set to 750 because the population of Winnipeg was around 750,000 at the time
n<- 750

#The longitude and latitude of Portage and Main
mu<-c(49.8955,-97.1385)          
sig<- matrix(c(0.006157, 0, 0, 0.0035),nrow=2,ncol=2,byrow=TRUE)


#Creating a multivariate normal distribution of sample points, which represent people. We will use these points and their distances from each other to simulate disease spread.
samples <-rmvnorm(n,mu,sig)

plot(samples[, 2], samples[, 1], xlab = "Longitude", ylab="Latitude", main="Map of Winnipeg")
```




Bivariate Normal with Regions
```{r}
#Dividing Winnipeg into four sections/strata based on longitude and latitude
longitudeNW=c(49.9, 49.9,  50.2, 50.2, 49.9)
latitudeNW=c(-97.323, -97.138483, -97.138483, -97.323, -97.323)
coordinatesNW=data.frame(longitudeNW, latitudeNW)


longitudeNE=c(49.9, 49.9, 50.2, 50.2,  49.9)
latitudeNE=c(-97.138483, -96.94, -96.94, -97.138483, -97.138483)
coordinatesNE=data.frame(longitudeNE, latitudeNE)


longitudeSW=c(49.9, 49.9, 49.615, 49.615,  49.9)
latitudeSW=c(-97.138483, -97.323, -97.323, -97.138483,  -97.138483)
coordinatesSW=data.frame(longitudeSW, latitudeSW)


longitudeSE=c(49.9, 49.9, 49.615, 49.615, 49.9)
latitudeSE=c(-97.138483, -96.94, -96.94, -97.138483, -97.138483)
coordinatesSE=data.frame(longitudeSE, latitudeSE)


#Plot of Winnipeg divided into 4 Strata
plot(samples[, 2], samples[, 1], xlab = "Longitude", ylab="Latitude", main="Map of Winnipeg Split into Four Strata")
lines(x=coordinatesNW$latitudeNW, y=coordinatesNW$longitudeNW, col="black")
lines(x=coordinatesNE$latitudeNE, y=coordinatesNE$longitudeNE, col="black")
lines(x=coordinatesSW$latitudeSW, y=coordinatesSW$longitudeSW, col="black")
lines(x=coordinatesSE$latitudeSE, y=coordinatesSE$longitudeSE, col="black")



#This is the area where we will be randomly infecting the first point. The area we will be randomly infecting is evenly distributed across the 4 strata.

longitudeCenter=c(49.935508, 49.935508, 49.855508, 49.855508, 49.935508)
latitudeCenter=c(-97.118483, -97.158483, -97.158483, -97.118483, -97.118483)
coordinatesCenter=data.frame(longitudeCenter, latitudeCenter)

plot(samples[, 2], samples[, 1], xlab = "Longitude", ylab="Latitude", main="Area of First Infection")
lines(x=coordinatesCenter$latitudeCenter, y=coordinatesCenter$longitudeCenter, col="red", lwd=2)


plot(samples[, 2], samples[, 1], xlab = "Longitude", ylab="Latitude", main="Area of First Infection With Strata")
lines(x=coordinatesCenter$latitudeCenter, y=coordinatesCenter$longitudeCenter, col="red", lwd=2)
lines(x=coordinatesNW$latitudeNW, y=coordinatesNW$longitudeNW, col="black")
lines(x=coordinatesNE$latitudeNE, y=coordinatesNE$longitudeNE, col="black")
lines(x=coordinatesSW$latitudeSW, y=coordinatesSW$longitudeSW, col="black")
lines(x=coordinatesSE$latitudeSE, y=coordinatesSE$longitudeSE, col="black")
```



Random First Infection Function
```{r}
#Gets all the points in a square that is roughly in the center (the red square). This sets the boundaries of the area of first infection. 
#long_lat_df will be the dataframe containing the coordinates of all the points of Winnipeg.

centerPoints = function(long_lat_df){

  #long_lat_df[i,2] is longitude
  #long_lat_df[i,1] is latitude
  center_points_df = long_lat_df[(long_lat_df[, 2]<=-97.118483) & (long_lat_df[, 2]>-97.158483) & (long_lat_df[, 1]>49.855508) & (long_lat_df[, 1]<49.935508),]
  
  colnames(center_points_df)=c("Longitude", "Latitude")
  
  return(center_points_df)
}



#We'll be randomly adding or subtracting a pair of randomly generated uniform values, divided by 25 and 50 respectively, from the very center coordinate of the population which will give us a random coordinate. We will then measure which coordinate is closest to the newly generated random coordinate. The point that is closest to the newly generated random coordinate will be the first infected.
randomInfect=function(df){
  
  #Gets all the points in a square that is roughly in the center (the red square).
  center_points=centerPoints(df)

  
  #Gets the row positions of all the center-points within the dataframe. This gets all the points within the area of first infection, which is the red square.
  centerPlacements= which((df[, 2]<=-97.118483) & (df[, 2]>-97.158483) & (df[, 1]>49.855508) & (df[, 1]<49.935508))
  
  
  #Picking a random coordinate to infect first
  longitude_shift=runif(1, -1, 1)    #min=-1, and max=1 so we can randomly subtract or add
  latitude_shift=runif(1, -1, 1)
  
  longitude_shift=(4*longitude_shift)/100
  latitude_shift=(2*latitude_shift)/100
  
  randomShift=c(longitude_shift, latitude_shift)
  
  
  #Gets the very center of the square
  centerCoordinate=c(-97.138483, 49.895508)
  
  
  
  #Whichever point is closest to this coordinate here will be first infected
  random_first_infect_coordinate=centerCoordinate+randomShift
  
  
  longitude_distances=center_points[,1]-random_first_infect_coordinate[1]
  latitude_distances=center_points[,2]-random_first_infect_coordinate[2]

  abs_val_longitude_distances=abs(longitude_distances)
  abs_val_latitude_distances=abs(latitude_distances)
  
  
  #Getting the sums of the absolute values of the distances from the points to the coordinates of first infection
  sum_distances = abs_val_longitude_distances + abs_val_latitude_distances

  
  #Gets the lowest sum of the absolute values of the coordinates. The coordinate with the lowest sum will be our first infected point. This is because it will have the least distance from the coordinate chosen to assign a first infection.
  place=centerPlacements[which.min(sum_distances)]
  
  #returns the placement of the closest point so we can infect them
  return(place)                    
}
```



These two functions were made by my professor. He allowed us to use them for our project.
Geometric and Exponential Epidemic Model Functions
```{r}
#An infected person will remain infectious for 3 time points
#We will be simulating 20 time points after the first infection

#Geometric Model
epigenGeometric <-function(pop,alpha,beta,interval){
  x <-pop[,1]
  y <- pop[,2]
  length <- nrow(pop)
  id <- 1:length
  inftime <- rep(0, length)

  distance <- inftime
  k <- randomInfect(pop)
  inftime[k] <- 1
  for(T in 1:interval){
    for(i in 1:length){
      if(inftime[i]==0){
        d<-0
        for(j in 1:length){
          if(inftime[j]!=0 && inftime[j] <= T &&inftime[j]>=(T-2)){
            distance[i] <-sqrt((x[i]-x[j])^2+(y[i]-y[j])^2)
            d <- d+ distance[i]^(-beta)
          }
        }
        pit <- 1-exp(-alpha*d)
        u <- runif(1,0,1)
        if(pit > u){
          inftime[i] <-T+1
        }
      }
    }
  }
  epidemic <- data.frame(id, x, y, inftime)
  return(epidemic)
}


#Exponential Model
epigenExponential <-function(pop,alpha,beta,interval){
  x <-pop[,1]
  y <- pop[,2]
  length <- nrow(pop)
  id <- 1:length
  inftime <- rep(0, length)

  distance <- inftime
  k <- randomInfect(pop)
  inftime[k] <- 1
  for(T in 1:interval){
    for(i in 1:length){
      if(inftime[i]==0){
        d<-0
        for(j in 1:length){
          if(inftime[j]!=0 && inftime[j] <= T &&inftime[j]>=(T-2)){
            distance[i] <-sqrt((x[i]-x[j])^2+(y[i]-y[j])^2)
            
            d <- d+ exp(distance[i]*(-beta))
          }
        }
        pit <- 1-exp(-alpha*d)
        u <- runif(1,0,1)
        if(pit > u){
          inftime[i] <-T+1
        }
      }
    }
  }
  epidemic <- data.frame(id, x, y, inftime)
  return(epidemic)
}
```



Colouring the Plot for Different Regions
```{r}
#In this function, we assume that we will have called a plot before calling these functions.

#long_coords and lat_coords mean longitude coordinates and latitude coordinates
map_severity = function(num_infected, long_coords, lat_coords){
  
  #No infected people in a region
  if(num_infected==0){
    polygon(x=lat_coords, y=long_coords, col="white")
  }
  
  #1 to 48 infected people in a region
  else if((num_infected>=1)&&(num_infected<=48)){
    polygon(x=lat_coords, y=long_coords, col="green")
  }
  
  #49 to 97 infected people in a region
  else if((num_infected>=49)&&(num_infected<=97)){
    polygon(x=lat_coords, y=long_coords, col="yellow")
  }
  
  #98 to 145 infected people in a region
  else if((num_infected>=98)&&(num_infected<=145)){
    polygon(x=lat_coords, y=long_coords, col="orange")
  }
  
  #More than 145 infected people in a region
  else{
    polygon(x=lat_coords, y=long_coords, col="red")
  }
}
```


Plot Displaying Functions
```{r}
#Displays heat maps
heatMapDisplayer=function(modulo, remainder, lowerLimit, lastNumber, inftime, df, titles){
  for(i in 1:lastNumber){
    if(((i%%modulo)==remainder)&&(i>1)||(i==lastNumber)){
      
      totalPerStrata=strataTotalInfectedPerTimePoint(inftime, df, i)
      
      plot(df[, 2], df[, 1], xlab = "Longitude", ylab="Latitude")
      title(main=titles[i-2])
      
      lines(x=coordinatesNW$latitudeNW, y=coordinatesNW$longitudeNW, col="purple")
      mapSeverityNW(totalPerStrata[3])
      
      lines(x=coordinatesNE$latitudeNE, y=coordinatesNE$longitudeNE, col="green")
      mapSeverityNE(totalPerStrata[4])
      
      lines(x=coordinatesSW$latitudeSW, y=coordinatesSW$longitudeSW, col="orange")
      mapSeveritySW(totalPerStrata[2])
      
      lines(x=coordinatesSE$latitudeSE, y=coordinatesSE$longitudeSE, col="blue")
      mapSeveritySE(totalPerStrata[1])
      
      par(xpd=TRUE)
      legend(x=-97.045, y=50.2, legend=c("0 Infections","1-48 Infections","49-97 Infections", "98-145 Infections", "145 or more Infections"), fill = c("white", "green", "yellow", "orange", "red"), cex=0.75)
    }
  }
}


#Displays infection maps
activeInfectionsDisplayer=function(modulo, remainder, lowerLimit, lastNumber, inftime, pop, title){
  for(i in 1:lastNumber){
    if(((i%%modulo)==remainder)&&(i>lowerLimit)||(i==lastNumber)){
      tMinusTwo= which(inftime==(i-2))
      tMinusOne= which(inftime==(i-1))
      t= which(inftime==(i))
      
      plot(pop[, 2], pop[, 1], xlab="Longitude", ylab="Latitude")
      title(main=title[i-2])
      points(pop[tMinusTwo,2], pop[tMinusTwo,1], pch=20, col="purple")
      points(pop[tMinusOne,2], pop[tMinusOne,1], pch=20, col="pink")
      points(pop[t,2], pop[t,1], pch=20, col="blue")
      
      
      #i>=5 as that is the minimum amount of time that someone will have recovered, and that is within our plot cycle of 2
      if(i>=5){  
        recovered = which((infected>=1) & (infected<(i-2)))
        points(pop[recovered,2], pop[recovered,1], pch=20, col="black")
      }
      leg=c("Infected 2 TPA", "Infected 1 TPA", "Newly Infected", "Recovered")
      legend(x=-97.03, y=50.2, legend=leg, pch=20, col=c("purple", "pink", "blue", "black"))
    }
  }
}
```



Finding the population of each strata, and finding the number of infected people in each strata
```{r}
#Finds the total population of each strata. Can use to find the total number of people in Winnipeg, and the total number of people infected in each strata
pop_of_strata=function(long_lat_df){
  
  total_SE = nrow(which((long_lat_df[,2] >= -97.138483) & (long_lat_df[,1]<=49.9)))
  total_NE = nrow(which((long_lat_df[,2] >= -97.138483) & (long_lat_df[,1]>49.9)))
  
  total_SW = nrow(which((long_lat_df[,2] <= -97.138483) & (long_lat_df[,1]<=49.9)))
  total_NW = nrow(which((long_lat_df[,2] <= -97.138483) & (long_lat_df[,1]>49.9)))
  
  population=c(total_SE, total_SW, total_NW, total_NE)
  return(population)
}
pop_of_strata(samples)

#193 people live in the southeast; 181 people live in the southwest; 187 people live in the northwest; 189 people live in the northeast. 



#Set lowerLimit to null to get how many have contracted the disease at and before a time point

#If lowerLimit isn't null, gets how many are infected in a specified interval of time
strata_infected = function(infections, samps, lowerLimit, upperLimit) {
  
  if (is.null(lowerLimit)){
    #Filter infections below the time limit
    valid_infections = (infections <= upperLimit)
  }
  
  else{
    #Filter infections within the time range
    valid_infections = (infections >= lowerLimit) & (infections <= upperLimit)
  }
  
  
  #Subset samps where infections are within the time range
  valid_samps = samps[valid_infections, drop = FALSE]

  
  #Sometimes R collapses valid_samps into a vector. The if statement below is for correcting when this does happen
  if (is.null(dim(valid_samps))) {
    valid_samps <- matrix(valid_samps, ncol = 2)
   }
  
  longitude = -97.138483
  latitude = 49.9
  
  
  
  #Infection counts per region
  SE = sum((valid_samps[, 2] >= longitude) & (valid_samps[, 1] <= latitude), na.rm = TRUE)
  NE = sum((valid_samps[, 2] >= longitude) & (valid_samps[, 1] > latitude), na.rm = TRUE)
  SW = sum((valid_samps[, 2] < longitude) & (valid_samps[, 1] <= latitude), na.rm = TRUE)
  NW = sum((valid_samps[, 2] < longitude) & (valid_samps[, 1] > latitude), na.rm = TRUE)
  
  
  infected=c(SE, SW, NW, NE)
  return(infected)
}
```



Epidemic Summary Functions
```{r}
#Finds the length of an epidemic by seeing if there are any active infections in the strata. This function is to be used in a loop.
#The first time point without any active infections in any strata will be declared the length of the epidemic. If an epidemic still has active infections at time point 20, time point 20 will be the length of the epidemic.

epiLength=function(infected_per_region, upperLimit){
  
  #Renaming the variable for clarity 
  ipr = infected_per_region
  
  #Runs true if no one is infected in any of the strata/
  if((ipr[1]==0)&&(ipr[2]==0)&&(ipr[3]==0)&&(ipr[4]==0)){
    return(upperLimit)
  }
  
  #The disease has not stopped spreading throughout the simulation. So, we say the epidemic length of that disease is 20.
  else if(upperLimit==20){
    return(upperLimit)
  }
  
  #Returns 0, meaning to continue the epidemic simulation
  else{
    return(0)
  }  
}


#Finds the peak of an epidemic by finding the time point with the most new infections.
peak=function(inftime, time){
  
  #Will be a count of the infections at each time point
  count=NULL
  
  
  for(i in 1:time){
    tempCount = sum(inftime == i)
    count=c(count, tempCount)
  }
  
  #Will store the number of infections. Number of infections can't be negative, so start it at -1
  highest=-1
  
  
  #Saves which time point has the most infections
  placement=NULL           
  for(i in 1:length(count)){
    num_infections=count[i]
    

    if(num_infections>highest){
      highest=num_infections
      placement=i
    }
  }
  return(placement)
}



#Prints 5 values which summarize the course of an epidemic
epiSummary=function(samps, inftime, time){

  
  #3 because that is the minimum amount of time for an epidemic to die out
  for(upper_limit in 3:time){
    lower_limit = upper_limit - 2
    activeInfected=strata_infected(inftime, samps, lower_limit, upper_limit)
    
    length=epiLength(activeInfected, upper_limit)
    
    
    #If length is 0, breaks out of the for loop as the epidemic ended
    if(length!=0){
      #Stops the loop as the epidemic has ended
      break            
    }
  }
  totalPerStrata=strata_infected(inftime, samps, NULL, time)
  total_infected=sum(totalPerStrata)
  
  top=peak(inftime, time)
  
  
  #Returns a summary of the epidemic
  summary=c(top, length, total_infected)
  return(summary)
}
```



Epidemic Simulating Functions
```{r}
#Samps, is our dataframe of x and y coordinates; replications is how many epidemics we want to generate; alpha and beta are the infection kernel parameters; time is how long we want an epidemic to run for.
#set exponential_simulation to true if you want to simulate an exponential distribution of a pandemic, and false if you want a geometric distribution of one.
epi_simulator=function(samps, replications, alpha, beta, time, exponential_simulation){

  total_peak=0; total_epi_length=0; total_total_infection=0
  
  for(h in 1:replications){
    
    if (exponential_simulation==TRUE){
      epidemic=epigenExponential(samps, alpha, beta, time)
    }
    
    else{
      epidemic=epigenGeometric(samps, alpha, beta, time)
    }
    
    epidemicSummary=epiSummary(samps, epidemic$inftime, time)
    
    
    total_peak=total_peak+epidemicSummary[1]
    total_epi_length=total_epi_length+epidemicSummary[2]
    total_total_infection=total_total_infection+epidemicSummary[3]
  }
  
  #Gets the average peak, length and number of infections across all epidemics
  avgPeak=total_peak/replications
  avgEpiLength=total_epi_length/replications
  avgTotalInfection=total_total_infection/replications
  
  
  summary=c(alpha, beta, avgPeak, avgEpiLength, avgTotalInfection)
  return(summary)
}
```



Plot Displaying Functions for Both Geometric and Exponential Distributions
```{r}
#The three functions below are very similar. The only difference is that the colour of the lines of the plots are different.
#plot_colour is a string, which will be the colour that you want the plot to be


#Replications dictates how many epidemics you want to simulate
#Set exponential_simulation to true if you want to simulate an exponential distribution of a pandemic, and false if you want a geometric distribution of one.
epi_plot=function(samps, replications, alpha, beta, time, plot_colour, exponential_simulation){
  
  
  for(h in 1:replications){
    
    if (exponential_simulation==TRUE){
      epidemic=epigenExponential(samps, alpha, beta, time)
    }
    
    else{
      epidemic=epigenGeometric(samps, alpha, beta, time)
    }
    
    infection_time=epidemic$inftime
    inftimes=NULL

    
    for(i in 1:time){
      count=sum(infection_time==i)
      inftimes=c(inftimes, count)
    }
    
    #We do this if statement so our plot is properly labelled
    if(h!=1){
      par(new=TRUE)
      plot(inftimes, type="l", col=plot_colour, xaxt='n', yaxt='n', ann=FALSE, ylim=c(0,200))
    }
    #Labels the x and y axis
    else{
      par(new=TRUE)
      plot(inftimes, type="l", col=plot_colour, ann = FALSE, ylim=c(0,200))
    }
  }
}
```




Function to simulate both geometric and exponential distributions
```{r}
#samps will be the points
#alpha will be the alpha value(s). set alpha to be just one value if you want it to be fixed
#beta will be the beta value(s). set beta to be just one value if you want it to be fixed
#epi_length will be a number, and dictates the length of each epidemic
#is_exp_epi is a boolean, and will instruct whether the epidemic was geometrically or exponentially created
epi_sims = function(samps, num_epidemics, alphas, betas, epi_length, is_exp_epi){
  
  epi_dataframe = data.frame(row.names = c("alpha", "beta", "Average Peak", "Average Epi Length", "Average Infections"))
  
  
  colnames_epi_df = c()
  
  
  #Records how many times the loops have executed. Necessary to correctly input data into epi_dataframe
  iteration = 0
  
  for(i in 1:length(alphas)){
    for(j in 1:length(betas)){
      
      iteration = iteration + 1
       colnames_epi_df = c(colnames_epi_df, paste0("Epi ", iteration, " alpha=", alphas[i], " beta=", betas[j]))

      
      
      epi = epi_simulator(samps, num_epidemics, alphas[i], betas[j], epi_length, is_exp_epi)
      epi_dataframe[iteration] = epi
    }
  }
  colnames(epi_dataframe) = colnames_epi_df
  return(epi_dataframe)
}
```



Geometric Epidemic Curves Beta( Beta = 0.0005) Fixed
```{r}
#Betas Fixed
set.seed(3000)
epi_plot(samples, 100, 0.001, 0.0005, 20 ,"red", F)
epi_plot(samples, 100, 0.0015, 0.0005, 20 ,"green", F)
epi_plot(samples, 100, 0.002, 0.0005, 20 ,"blue", F)
title(main = "3x100 Geometric Epidemic Curves", xlab = "Time Point", ylab="Infections"); legend("topleft", legend=c("alpha=0.001", "alpha=0.0015", "alpha=0.002"), lwd=1, col=c("red", "green", "blue"), cex=0.75)
```



Geometric Epidemic Curves Alpha (Alpha = 0.001) Fixed
```{r}
set.seed(3000)
epi_plot(samples, 100, 0.001, 0.001, 20, "red", F)
epi_plot(samples, 100, 0.001, 0.0015, 20, "green", F)
epi_plot(samples, 100, 0.001, 0.002, 20, "blue", F)
title(main = "3x100 Geometric Epidemic Curves", xlab = "Time Point", ylab="Infections"); legend("topleft", legend=c("beta=0.001", "beta=0.0015", "beta=0.002"), lwd=1, col=c("red", "green", "blue"), cex=0.75)
```






Result Tables for Geometric Curves
```{r}
#Same betas( beta=0.0005), different alphas
set.seed(3000)


geo_alpha_values = c(0.001, 0.0015, 0.002)
geo_beta_fixed = epi_sims(samples, 100, geo_alpha_values, 0.0005, 20, F)
geo_beta_fixed


geo_beta_values = c(0.001, 0.0015, 0.002)
geo_alpha_fixed = epi_sims(samples, 100, 0.001, geo_beta_values, 20, F)
geo_alpha_fixed
```



Exponential Epidemic Curves Beta (Beta = 0.0005) Fixed
```{r}
#Betas Fixed
set.seed(3000)
epi_plot(samples, 100, 0.001, 0.0005, 20, "red", T)
epi_plot(samples, 100, 0.0015, 0.0005, 20, "green", T)
epi_plot(samples, 100, 0.002, 0.0005, 20, "blue", T)
title(main = "3x100 Exponential Epidemic Curves", xlab = "Time Point", ylab="Infections"); legend("topleft", legend=c("alpha=0.001", "alpha=0.0015", "alpha=0.002"), lwd=1, col=c("red", "green", "blue"), cex=0.75)
```




Exponential Epidemic Curves Alpha (Alpha = 0.001) Fixed
```{r}
set.seed(3000)
epi_plot(samples, 100, 0.001, 0.001, 20, "red", T)
epi_plot(samples, 100, 0.001, 0.0015, 20, "green", T)
epi_plot(samples, 100, 0.001, 0.002, 20, "blue", T)
title(main = "3x100 Exponential Epidemic Curves", xlab = "Time Point", ylab="Infections"); legend("topleft", legend=c("beta=0.001", "beta=0.0015", "beta=0.002"), lwd=1, col=c("red", "green", "blue"), cex=0.75)
```




Result Tables for Exponential Curves
```{r}
#Same betas, different alphas
set.seed(3000)

exp_alpha_values = c(0.001, 0.0015, 0.002)
exp_beta_fixed = epi_sims(samples, 100, exp_alpha_values, 0.0005, 20, T)
exp_beta_fixed


exp_beta_values = c(0.001, 0.0015, 0.002)
exp_alpha_fixed = epi_sims(samples, 100, 0.001, exp_beta_values, 20, T)
exp_alpha_fixed

```


Infected Title and Heat Map Generator Function
```{r}
title_generator = function(is_exp, is_heat_map, start_time, end_time){
  
  title_start = ifelse(is_exp, "Exponential", "Geometric")
  middle_phrase = ifelse(is_heat_map, "Heat Map", "Plot of SIR Individuals")

  
  titles = c(rep("", end_time - start_time + 1))
  for(time_point in start_time:end_time){
    
    #Runs true if time_point is odd, or if time_point is the last time
    if ((time_point%%2 == 1) | time_point == end_time){
      titles[time_point - start_time + 1] = paste0(title_start, " ", middle_phrase,  " at Time Point ", time_point)
    }
    
  }
  return(titles)
}
```

Note: I didn't include these plots in the report for geometric or exponential as there were too many plots to include.
Geometric Heat Maps and Maps of Infected Individuals
```{r}
#Setting the titles that we will use for the plots
infectedTitleGeo = title_generator(F, F, 3, 20)
heatMapTitleGeo = title_generator(F, T, 3, 20)


set.seed(3001)
epigenGeo=epigenGeometric(samples, 0.001, 0.0005, 20)
activeInfectionsDisplayer(2, 1, 1, 20, epigenGeo$inftime, samples, infectedTitleGeo)
heatMapDisplayer(2, 1, 1, 20, epigenGeo$inftime, samples, heatMapTitleGeo)
```


Note: I didn't include these plots in the report for geometric or exponential as there were too many plots to include.
Exponential Heat Maps and Maps of Infected Individuals
```{r}

#Setting the titles that we will use for the plots
infectedTitleExp = title_generator(T, F, 3, 20)
heatMapTitleExp = title_generator(T, T, 3, 20)

set.seed(3001)
epigenExp=epigenExponential(samples, 0.001, 0.0005, 20)
activeInfectionsDisplayer(2, 1, 1, 20, epigenExp$inftime, samples, infectedTitleExp)
heatMapDisplayer(2, 1, 1, 20, epigenExp$inftime, samples, heatMapTitleExp)
```



